Symmetric Peer-to-Peer Applications

### 2022-10-13 tpd-22.tex
- baks figure

In this section, we evaluate if (and to what extent) our design meets its goals
to ensure that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
%
We simulate an application varying the network latency and churn, as well as
the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the recoverability from churns, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We then count all time travel occurrences during the simulation.
%
Regarding (b), we use an absolute simulation clock to track, in real time, the
execution pace of each peer.
% in comparison to the reference peer, which is the one most advanced in time.
We then count the mismatches between the clocks.
%
Regarding (c), we make peers leave and join the network periodically, possibly
creating partitions.
We then assert that they all catch up in real time.

@@

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with peers organized in straight lines and cycles.
%
In order to have an absolute clock, we use a single machine to simulate all
peers, allowing us to merge their logs into a single file with a comparable
shared timeline.
%
We simulate the network latency in software with random delays.

Figure~\ref{TODO} results...
- colors indicate feasibility

We now detail how we instrument the middleware implementation to measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
TODO: in the figure, we consider range a-b, c-d...
%
\item \textbf{Real-time pace of peers:}
Every time a peer receives \code{SYNC} packets and is behind, we output its id
and how much ticks it needs to fast forward.
At the end, we measure the percentage of the sum of all forward ticks over the
total simulation ticks (\code{TODO} in Figure~\ref{TODO}).
As an example, if all peers sum $1000$ forward ticks over $100k$ accumulated
simulation ticks, then the final measure is $1\%$.
%
We also start each peer with a random delay of up to $10s$ to force a
synchronization mismatch from the beginning.
%
Each peer outputs its current tick continuously, allowing us to compare them
in the shared timeline.
Each time we see a greater tick never seen in the timeline before, we count
smaller ticks from other peers (considering latency), which would constitute
time violations (\code{TODO} in Figure~\ref{TODO}).
We expect this counter to be close to zero even considering the whole
simulation.
TODO: in the figure, we consider range a-b, c-d...
TODO: in comparison to the reference peer, which is the one most advanced in time.
%
\item \textbf{Correctness of unstable peers:}
We run a separate simulation in which, for every $100s$, each peer remains
$40s$ online and $20s$ offline, including peers \code{9--11} in the middle of
the network.
This creates partitions in which sides advance in time and generate events out
of sync, which need to be merged and resynchronized constantly.
We measure
    - state (even for stable peers)
    - qto tempo leva para sync
TODO: in the figure, we consider range a-b, c-d...
%
\end{enumerate}

- ate 20
- 30: bugs
- 40: -> <- O(n), [500|500] future, (-5s) delay links

- qual a natureza do baksS alto e baksI baixo?

>>>>

In this section, we evaluate if (and to what extent) our design meets its goals
to ensure that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
%
We simulate an application varying the network latency and peer churn, as well
as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the recoverability from churns, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We then count all time travel occurrences during the simulation.
%
Regarding (b), we use an absolute simulation clock to track, in real time, the
execution pace of each peer.
% in comparison to the reference peer, which is the one most advanced in time.
We then count the mismatches between the clocks.
%
Regarding (c), we make peers leave and join the network periodically, possibly
creating partitions.
We then assert that they all catch up in real time within a short period.

@@

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with peers organized in straight lines and cycles.
The topology has an average of 5 hops between peers (e.g., \code{4--16} are 7
hops away).
%
In order to have an absolute clock, we use a single machine to simulate all
peers, allowing us to merge their logs into a single file with a comparable
shared timeline.
%
We use \emph{NetEm}~\cite{netem} to simulate the network latency with a normal
distribution (e.g., \code{tc qdisc add dev lo root netem delay 200ms 40ms
distribution normal}).
%
We vary
    (i)   the network latency (\code{5--500ms} between each peer),
    (ii)  the rate of events (\code{5--200 evt/sec} in the whole network), and
    (iii) the delay multiplier (\code{1--5x} considering the latency and the
          average hops between peers).
Regarding item (c), a \code{50ms} latency with a \code{2x} multiplier results
in \code{500ms} event delays, i.e., each event is triggered with this delay to
compensate the given latency and fixed average of 5 hops.
%
These variations result in $108$ combinations.
We executed each combination $3$ times for $5$ minutes each.
Therefore, the experiments take $27$ hours to complete.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{baks}
  \caption{
    \label{fig.baks}
The \code{5x}, \code{2x}, and \code{1x} delay regions each contains $36$
measures for multiple configurations of event rate (\code{5--200evt/min} and
network latency (\code{5--500ms}).
%
The color thresholds (\emph{white}, \emph{yellow}, \emph{red}, \emph{black})
are arbitrary but help to distinguish between regions of interest.
%
The experiments uses $1$ process for each peer in a single Linux machine
(\emph{i7/16GB}).
\end{figure*}

We now detail the results and how we instrument the middleware implementation
to measure the properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks.
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
Figure~\ref{fig.baks} presents the results considering all combinations of
\code{(i)}, \code{(ii)}, and \code{(iii)} above.
The colors indicate the feasibility of each tested scenario
    (\emph{white=good}, \emph{yellow=moderate}, \emph{red=poor},
    \emph{black=faulty}).
%
For instance, the three rectangles labelled \code{(1)} represent a scenario
with $50ms$ network delay, generating $25evt/min$.
Each rectangle uses a different delay multiplier, showing a good performance
for \code{5x}, moderate for \code{2x}, and poor for \code{1x}.
%
The color patterns indicate clear boundaries for the scenarios that can meet
event deadlines with the desired performance.
%
\item \textbf{Real-time pace of peers:}
All peers output their current ticks continuously, allowing us to compare them
in the shared timeline.
Every time we see a greater tick never seen in the timeline before, we count
smaller ticks from other peers, which constitute time violations.
As an example, if all peers sum $1000$ of such smaller ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
We also start each peer with a random delay of up to $10s$ to force a
synchronization mismatch at the beginning.
%
Considering all scenarios, the average is negligibly under $0.2\%$, with no
variations.
Therefore, we do not show the resulting table (such that of
Figure~\ref{fig.baks}), which would not provide further insights.
%
\item \textbf{Correctness of unstable peers:}
We run a separate simulation in which, for every $100s$, each peer remains
$40s$ online and $20s$ offline, including peers \code{9--11} in the middle of
the network.
This creates partitions in which sides advance in time and generate events out
of sync, which need to be merged and resynchronized constantly.
We measure
    - state (even for stable peers)
    - qto tempo leva para sync
TODO: in the figure, we consider range a-b, c-d...
%
\end{enumerate}

This could represent a...
As an example of a concrete scenario, an interactive class over the Internet
could have
    an RTT of \emph{50--200ms} (\emph{Latency}),
    interacting every \emph{5s} (\emph{Rate}).
%e.g., a slide advance).
